Generalized Tractability

### 2023-03-23 GeneralizedTractability_230310.tex
Updates from Overleaf

\begin{theorem}\label{thm_main_strong_tract2}
A problem is strongly $T$-tractable iff there exists $\vp \in [\vzero, \boldsymbol{\infty})$ and an integer $L(\vp) > 0$ such that
\begin{equation} \label{eq:strong_tractiff3}
     S(\vp):=\sup_{d \in \naturals} \sum_{i = L(\vp)}^\infty \frac{1}{T(\lambda_{i,d}^{-1},1,\vp)} < \infty.
\end{equation}
If \eqref{eq:strong_tractiff3} holds for some $\vp$, let  $\widetilde{\cp}_{\textup{strct}} : = \{\vp^* : \eqref{eq:strong_tractiff3} \text{ holds }\forall \vp \in (\vp^*,\boldsymbol{\infty})\}$.  Then $\cp_{\textup{strct}} = \widetilde{\cp}_{\textup{strct}}$, and the set of optimal strong tractability parameters is
\[
	\cp_{\textup{sopt}} =
	\{\vp^* \in \widetilde{\cp}_{\textup{strct}} :  \vp* \notin [\vp^\dagger,\boldsymbol{\infty}) \ \forall \vp^\dagger \in  \widetilde{\cp}_{\textup{strct}} \setminus \{\vp^*\} \}.
\]
\end{theorem}

@@

Now we take this upper bound further, specializing to the case of $d'=1$:
\begin{align*}
       \comp(\varepsilon,d)
       & = 1 + T(\varepsilon^{-1},1, \vp) \Biggl [ \sum_{i=1}^{L(\vp)-1} \frac{1}{T(\lambda_{i, d}^{-1},1,\vp)}
       + \underbrace{\sum_{i=L(p)}^\infty \frac{1}{T(\lambda_{i, d}^{-1},1,\vp)}}_{\le S(p) <\infty\ \text{by \eqref{eq:strong_tractiff3}} }\Biggr] \\
       & \le 1+ T(\varepsilon^{-1},1,\vp) \underbrace{\left[\frac{(L(p)-1)}{T(\lambda_{\max}^{-1},1,\vp)} + S(\vp)\right]}_{=:C_1(\vp)}\\
       & = 1+ T(\varepsilon^{-1},1,\vp) C_1 (p)\\
       &\le C_{\vp} T(\varepsilon^{-1},1,\vp),
\end{align*}
for some suitably chosen $C_{\vp}>0$. This means that we have strong $T$-tractability via \eqref{eq:strong_tract_def}, and verifies sufficiency of \eqref{eq:strong_tractiff3}.

@@

For $\varepsilon$ taking on all positive values, $j(\varepsilon,\vp)$ takes on all values greater than or equal to $L(\vp)$, so
\[
j\le C_{\vp}\, T(\varepsilon^{-1},1,\vp)+1 \le C_{\vp} T(\lambda_{j,d}^{-1},1,\vp)+1, \qquad \forall j \ge L(\vp).
\]
This implies via our technical assumption \eqref{eq:ptauassume} that
\begin{equation*}
 K_{\vp,\tau}\,T (\lambda_{j,d}^{-1},1,\tau \vp) \ge
 [T(\lambda_{j,d}^{-1},1, \vp)]^\tau
 \ge
  \left[\frac{(j-1)}{C_{\vp}}\right]^\tau \qquad \forall j \ge L(\vp)
\end{equation*}
Summing both sides of the inequality yields it follows that
\begin{equation*}
\sup_{d\in\naturals} \sum_{j=j (\infty,\vp)}^\infty \frac{1}{T (\lambda_{j,d}^{-1},1, \tau \vp)}
\le K_{\vp,\tau}\, C_{\vp}^\tau
\sum_{j=j (\infty,\vp)}^\infty \frac{1}{(j-1)^\tau} \le
K_{\vp,\tau}\, C_{\vp}^\tau\, \zeta (\tau) < \infty,
\end{equation*}
where $\zeta$ denotes the Riemann zeta function.
This yields \eqref{eq:strong_tractiff3} with $\vp$ replaced by $\vp' = \tau \vp$ and $L(\vp') = j (\infty,\vp)$, and so we see the necessity of $\eqref{eq:strong_tractiff3}$.

@@

If $\vp^* \in \cp_{\textup{strct}}$, then \eqref{eq:strong_tract_def} holds for all $\vp \in (\vp^*,\vinfty)$.  By the argument to prove the necessary condition, it follows that \eqref{eq:strong_tractiff3} must also hold for all $\vp \in (\vp^*,\vinfty)$, so $\vp^* \in \widetilde{\cp}_{\textup{strct}}$.  Conversely, if $\vp^* \in \widetilde{\cp}_{\textup{strct}}$, then \eqref{eq:strong_tractiff3}  holds for all $\vp \in (\vp^*,\vinfty)$.  By the argument to prove the sufficient condition, it follows that \eqref{eq:strong_tract_def} must also hold for all $\vp \in (\vp^*,\vinfty)$, so $\vp^* \in \cp}_{\textup{strct}}$.

>>>>

\begin{theorem}\label{thm_main_strong_tract2}
A problem is strongly $T$-tractable iff there exists $\vp \in [\vzero, \boldsymbol{\infty})$ and an integer $L_{\vp} > 0$ such that
\begin{equation} \label{eq:strong_tractiff3}
     S(\vp):=\sup_{d \in \naturals} \sum_{i = L_{\vp}}^\infty \frac{1}{T(\lambda_{i,d}^{-1},1,\vp)} < \infty.
\end{equation}
If \eqref{eq:strong_tractiff3} holds for some $\vp$, let  $\widetilde{\cp}_{\textup{strct}} : = \{\vp^* : \eqref{eq:strong_tractiff3} \text{ holds }\forall \vp \in (\vp^*,\boldsymbol{\infty})\}$.  Then $\cp_{\textup{strct}} = \widetilde{\cp}_{\textup{strct}}$, and the set of optimal strong tractability parameters is
\[
	\cp_{\textup{sopt}} =
	\{\vp^* \in \widetilde{\cp}_{\textup{strct}} :  \vp* \notin [\vp^\dagger,\boldsymbol{\infty}) \ \forall \vp^\dagger \in  \widetilde{\cp}_{\textup{strct}} \setminus \{\vp^*\} \}.
\]
\end{theorem}

@@

Now we take this upper bound further, specializing to the case of $d'=1$:
\begin{align*}
       \comp(\varepsilon,d)
       & = 1 + T(\varepsilon^{-1},1, \vp) \Biggl [ \sum_{i=1}^{L_{\vp}-1} \frac{1}{T(\lambda_{i, d}^{-1},1,\vp)}
       + \underbrace{\sum_{i=L(p)}^\infty \frac{1}{T(\lambda_{i, d}^{-1},1,\vp)}}_{\le S(p) <\infty\ \text{by \eqref{eq:strong_tractiff3}} }\Biggr] \\
       & \le 1+ T(\varepsilon^{-1},1,\vp) \underbrace{\left[\frac{(L(p)-1)}{T(\lambda_{\max}^{-1},1,\vp)} + S(\vp)\right]}_{=:C_1(\vp)}\\
       & = 1+ T(\varepsilon^{-1},1,\vp) C_1 (p)\\
       &\le C_{\vp} T(\varepsilon^{-1},1,\vp),
\end{align*}
for some suitably chosen $C_{\vp}>0$. This means that we have strong $T$-tractability via \eqref{eq:strong_tract_def}, and verifies the sufficiency of \eqref{eq:strong_tractiff3}.

@@

For $\varepsilon$ taking on all positive values, $j(\varepsilon,\vp)$ takes on all values greater than or equal to $L(\vp)$, so
\[
j\le C_{\vp}\, T(\varepsilon^{-1},1,\vp)+1 \le C_{\vp} T(\lambda_{j,d}^{-1},1,\vp)+1, \qquad \forall j \ge L(\vp).
\]
This implies via our technical assumption \eqref{eq:ptauassume} that
\begin{equation*}
 K_{\vp,\tau}\,T (\lambda_{j,d}^{-1},1,\tau \vp) \ge
 [T(\lambda_{j,d}^{-1},1, \vp)]^\tau
 \ge
  \left[\frac{(j-1)}{C_{\vp}}\right]^\tau \qquad \forall j \ge L(\vp)
\end{equation*}
Summing both sides of the inequality yields it follows that
\begin{equation*}
\sup_{d\in\naturals} \sum_{j=j (\infty,\vp)}^\infty \frac{1}{T (\lambda_{j,d}^{-1},1, \tau \vp)}
\le K_{\vp,\tau}\, C_{\vp}^\tau
\sum_{j=j (\infty,\vp)}^\infty \frac{1}{(j-1)^\tau} \le
K_{\vp,\tau}\, C_{\vp}^\tau\, \zeta (\tau) < \infty,
\end{equation*}
where $\zeta$ denotes the Riemann zeta function.
This yields \eqref{eq:strong_tractiff3} with $\vp$ replaced by $\vp' = \tau \vp$ and $L_{\vp'} = j (\infty,\vp)$, and so we see the necessity of $\eqref{eq:strong_tractiff3}$.

@@

First we show  that if $\vp^* \in \cp_{\textup{strct}}$, then $\vp^* \in \widetilde{\cp}_{\textup{strct}}$.  If $\vp^* \in \cp_{\textup{strct}}$, then \eqref{eq:strong_tract_def} must hold for all $\vp' \in (\vp^*,\vinfty)$.  For any $\vp' \in (\vp^*,\vinfty)$, we may choose $\vp$ and $\tau$ such that $\vp^* < \vp < \vp' = \tau \vp$. Since $\vp > \vp^*$, \eqref{eq:strong_tract_def} also holds for $\vp$, and it follows that \eqref{eq:strong_tractiff3} must hold for $\vp'$ by the proof of necessity above.  Thus, $\vp^* \in \widetilde{\cp}_{\textup{strct}}$.

Next we show that if $\vp^* \in \widetilde{\cp}_{\textup{strct}}$, then $\vp^* \in \cp_{\textup{strct}}$.  If $\vp^* \in \widetilde{\cp}_{\textup{strct}}$, then \eqref{eq:strong_tractiff3}  holds for all $\vp \in (\vp^*,\vinfty)$.  By the argument to prove the sufficient condition above, it follows that \eqref{eq:strong_tract_def} must also hold for all $\vp \in (\vp^*,\vinfty)$. Thus, $\vp^* \in \cp}_{\textup{strct}}$.
